\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage[
    a4paper,
    left=5mm,
    right=5mm,
    top=5mm,
    bottom=0mm]{geometry}
\usepackage{enumitem}
\usepackage{lmodern}

\name{Cristóbal}{Contreras Beltrán}

\newcommand{\sectionMargin}{-3mm}
\newcommand*{\customcventry}[7][.13em]{
    \begin{tabular}{@{}l}
    {\bfseries #4} \
    {\itshape #3}
    \end{tabular}
    \hfill
    \begin{tabular}{l@{}}
    {\bfseries #5} \
    {\itshape #2}
    \end{tabular}
    \ifx&#7&%
    \else{\
    \begin{minipage}{\maincolumnwidth}%
    \small#7%
    \end{minipage}}\fi%
    \par\addvspace{#1}
}

\begin{document}

\makecvtitle

\vspace*{-11mm}

\begin{center}
    \textbf{Software Engineer Degree | Frontend Developer \& IT support}
\end{center}

\vspace*{-7mm}

\begin{center}
    \begin{tabular}{ c @{\hskip 1em} c @{\hskip 1em} c }
        \faMobile \enspace +56 9 9518 2311
        &
        \faEnvelope \enspace cristobal.contreras@outlook.cl
        &
        \faHome \enspace Labranza, Chile (high mobility)
    \\
        \faLinkedin\enspace
        \href{https://www.linkedin.com/in/cristobal-contreras-beltran/}{\underline{/in/cristobal-contreras}}
        &
        \faGithub\enspace
        \href{https://github.com/AsCraftC}{\underline{/AsCraftC}}
        &
        \faBehance\enspace
        \href{https://www.behance.net/AsCraftC}{\underline{/AsCraftC}}
    \end{tabular}
\end{center}

\vspace*{-10mm}

\section{Profile}{
  Frontend Developer with a strong background in \textbf{React}, \textbf{JavaScript}, \textbf{CSS}, \textbf{AstroJS}, and \textbf{UX/UI design}. Experienced in developing \textbf{responsive and user-friendly web applications}, integrating \textbf{RESTful APIs}, and implementing \textbf{modern frontend technologies}. Passionate about creating \textbf{efficient and aesthetically pleasing digital experiences}. Adept at working in \textbf{fast-paced environments}, collaborating with cross-functional teams, and continuously learning new technologies. In addition, I possess strong soft skills that allow me to help users to understand and resolve usability and/or technical issues. 
}

\vspace*{\sectionMargin}

\section{Technical Skills}{
\begin{itemize}[label=\textbullet, noitemsep]
  \item {\underline{\textbf{Programming Languages \& Frameworks:}} 
    {JavaScript (ES6+)},
    {React},
    {HTML5},
    {CSS3},
    {SASS},
    {Astro}
    {Vue3},
    {Java},
    {Springboot},
    {Flutter},
    {Unity},
    {Godot},
    {SQL},
    {Python},
    {C\#},
    {Arduino},
    {LateX}
  }
  \item {\underline{\textbf{UI/UX Design Tools:}}
    {Figma},
    {Wireframing},
    {Prototyping},
    {Responsive design},
    {User Centered Design (UCD)}
  }
  \item {\underline{\textbf{Web Development:}}
    {RESTful API},
    {Webpack},
    {npm},
    {SEO Optimization},
    {Browser Testing \& Debugging},
    {Accessibility (WCAG)}
  }
  \item {\underline{\textbf{Version Control \& Deployment:}}
    {git},
    {GitHub},
    {git flow},
    {Docker},
    {IEEE-830} requirement documentation,
    {UML},
    {CI/CD}
  }
  \item {\underline{\textbf{Database:}}
    {MySQL},
    {PostgreSQL},
    {MongoDB}
  }
  \item {\underline{\textbf{Other Technologies: }}
    {Office 365}  
    {VSCode},
    {Android Studio},
    {IntelliJ IDEA},
    {Windows Administrator} (7, 10, 11),
    {GNU/Linux} (Ubuntu, CentOS, ArchLinux, fedora, kali),
    {Risk management}
  }
  \item {\underline{\textbf{Additional Skills: }}
    {Encryption},
    {Unit Test},
    {Risk management},  
    {Self-management},
    {Class B} Driver License
  }
\end{itemize}}

\vspace*{\sectionMargin}

\section{Professional Experience}{
  \customcventry
  {02/2021 ‐ actual}
  {\href{http://www.tisol.cl/}{\underline{ASESORIAS Y GESTIONES TECNOLOGICAS SPA}}}
  {IT support,}
  {La Araucania, Chile}
  {}
  {{\begin{itemize}[leftmargin=0.6cm, noitemsep, label={\textbullet}]
      \item Diagnosed and repaired hardware and software issues for printers.
      \item Configured and validated printer usage on \textbf{LAN networks}.
      \item \textbf{Trained users} on printer equipment usability and best practices.
      \item Optimized printer usage, increasing user productivity and reducing technical intervention needs.
  \end{itemize}
  }
  }

  \vspace*{2mm}

  \customcventry
    {09/2024 ‐ 12/2024}
    {{ \href{https://www.araucaniasur.cl/index.php/hospital-de-villarrica/}{\underline{Villarrica Hospital}} }}
    {IT support,}
    {Villarrica, Chile}{}
    {{\begin{itemize}[leftmargin=0.6cm, noitemsep, label={\textbullet}]
        \item \textbf{Optimized user experience} and streamlined daily tasks through effective configuration and repair of institutional equipment.
        \item Enhanced employee comfort and efficiency by \textbf{configuring services, software, and office networks}.
        \item Implemented agile response strategies for \textbf{immediate problem resolution} at operational points.
        \item Expertly \textbf{administered, configured, and repaired Windows Office Systems} to ensure smooth operation.
    \end{itemize}}
  }

  \vspace*{2mm}

  \customcventry
  {06/2023 ‐ 12/2023}
  {\href{https://ideaufro.com/}{\underline{iDEAUFRO}}}
  {Frontend Developer,}
  {Temuco, Chile}{}
  {{\begin{itemize}[leftmargin=0.6cm, noitemsep, label={\textbullet}]
    \item Developed and maintained \textbf{Vue3-based web applications}, ensuring high performance and scalability
    \item Gathered and analyzed \textbf{frontend project requirements} to ensure alignment with client needs.
    \item Created \textbf{wireframes and prototypes in Figma}, iterating based on user feedback.
    \item Designed and implemented interactive UI components, improving user experience and engagement.
    \item Integrated \textbf{RESTful APIs} for seamless communication between frontend and backend services.
    \item Deployed applications using Docker and optimized for cross-browser compatibility.
  \end{itemize}}
  }
}

\vspace*{\sectionMargin}

\section{Education}
\customcventry
    {2018-2023}
    {\href{https://1drv.ms/b/c/13c8ae619d64655e/EV5lZJ1hrsgggBOHLAAAAAABHh9OZUbWLd2nx7PTa_OSsg?e=Fedmge}{\underline{Universidad de La Frontera}} }
    {Ingeniería civil Informática (Software Engineering)}
    {Temuco, Chile}
    {}{}
    {Relevant Courses: 
        Network Workshop, 
        Computer Science 1 y 2, 
        Databases 1 y 2, 
        Requirements engineering,
        Computer Auditing,
        UX/UI design,
        Cryptography and privacy,
        Software quality management,
        Project formulation and evaluation,
        Information Security,
        Internet of Things(IoT)
}

\vspace*{\sectionMargin}

\section{Certifications \& Online Courses}{
\begin{itemize}[label=\textbullet, noitemsep]
    \item Personal Cybersecurity Route (May. 2024) \href{https://1drv.ms/b/c/13c8ae619d64655e/EZYaMe6SBhJAshtvq4ORCQoBwWMYRerI4_xiuqXjORVd0w?e=I4tLqg}{\underline{Platzi}}
    \item Git \& GitHub Professional course (Jun. 2024) \href{https://1drv.ms/b/c/13c8ae619d64655e/EXeQGPrTCjFDpmx8pCItVTwB-OS1r-tkKJbmgYnahuxtYg?e=akKEsU}{\underline{Platzi}}
    % \item Learn Unity y C\# developing real games (May. 2024) - \underline{\color{blue}\href{https://www.udemy.com/}{Udemy}}
    % \item Power BI TOTAL in 14 Days - Advance Data Analyst (May. 2024) \underline{\color{blue}\href{https://www.udemy.com/}{Udemy}}
\end{itemize}
}

\vspace*{\sectionMargin}

\section{Languages}
\begin{tabbing}
  \texttt{d----x} \hspace{1mm}\= \textbf{English} \hspace{1mm}\= [B1] \\
  \texttt{drw--} \> \textbf{English} \> [Technical] \\
  \texttt{drwx} \> \textbf{Español} \> [Native] \\
  \** Linux Permissions Notation: r=Reading, w=Writing, x=Execute (Spoken)
\end{tabbing}
\end{document}